### 2016-04-22 Manuscript/SW_early_life_telomeres_tables_and_figures.Rmd
DSR edtis

Fig1A <- ggplot(temp,aes(x = Agemonths,y = RTL))+
  ylab('RTL') + 
  xlab('Age (months)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = 'none')+
  geom_point(col='grey')+
  stat_smooth(method = 'lm',col='darkgrey')+
  annotate('text',x = 1,y = 2.1,label = 'A')

@@

Fig1B <- ggplot(temp,aes(x = DeltaAge,y = RTL))+
  ylab('RTL') + 
  xlab(expression(Delta*' age (months)')) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = 'none')+
  geom_point(col='grey')+
  stat_smooth(method = 'lm',col = 'darkgrey')+
  annotate('text',x = -100,y = 2.1,label = 'B')

@@

Fig2 <- ggplot(temp,aes(x = LayYear,y = RTL))+
  ylab('RTL') + 
  xlab('Cohort') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12,angle = 90), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = 'top')+
  geom_jitter(col = 'grey')+
  geom_boxplot(outlier.colour = NA,notch=F,alpha=0.2)+
  scale_colour_manual(values = c('grey','darkorange'))+
  scale_fill_manual(values = c('grey','darkorange'))

@@

Fig3A <- forestplot(table2)+
  annotate('text',x = 0.8,y = 0.25,label = 'A')

@@

Fig3B <- ggplot(temp,
       aes(x = Tarsus,
           y = RTL,
           colour=`Age (months)`,
           fill = `Age (months)`,
           shape = `Age (months)`)) +
  ylab('RTL') + 
  xlab('Tarsus length (mm)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = 'top') +
  geom_point()+
  stat_smooth(method = 'lm')+
  scale_colour_manual(values = c('grey','darkorange','darkgreen'))+
  scale_fill_manual(values = c('grey','darkorange','darkgreen'))+
  annotate('text',x = 17,y = 2.1,label = 'B')

Fig3C <- ggplot(temp,
       aes(col = `Age (months)`,
           fill =  `Age (months)`,
           y = RTL,
           x=TQ)) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = 'top') +
  geom_point()+
  stat_smooth(method = 'lm')+
  scale_colour_manual(values = c('grey','darkorange','darkgreen'))+
  scale_fill_manual(values = c('grey','darkorange','darkgreen'))+
  annotate('text',x = 3,y = 2.1,label = 'C')

@@

Fig4A <- ggplot(temp,
       aes(x = RTL,
           y = RTL1,
           col=`Age (months)`)) +
  ylab('Adult RTL') + 
  xlab('Juvenile RTL') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = c(0.9,0.9),
        legend.background = element_rect(fill = grey(0.9))) +
  geom_point()+
  scale_colour_manual(values = c('grey','darkorange','darkgreen'))+
  scale_fill_manual(values = c('grey','darkorange','darkgreen'))+
  annotate('text',x = 0,y = 2.1,label = 'A')

Fig4B <- ggplot(temp,
       aes(x = `Age (months)`,
           y = Loss)) +
  ylab(expression(Delta*'RTL')) + 
  xlab('Age (months)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = 'top') +
  geom_boxplot(outlier.shape = NA)+
  geom_jitter(col = 'grey')+
  annotate('text',x = 0.5,y = 1.5,label = 'B')+
  geom_abline(slope = 0,intercept = 0,lty = 2)

temp <- Loss
#Run the model
lm2 <- lmer(Loss ~ Agemonths+Helper+Tarsus + NonHelper + Sex + BodyMass  + TQ + (1|FieldPeriodID),
            data = temp,
            REML = FALSE)
lm2 <- standardize(lm2)

@@

Fig4C <- forestplot(table2)+
  annotate('text',x = 0.75,y = 0.6,label = 'C')

@@

```{r Figure 5}
temp <- subset(juv13,Agemonths != 1)
temp$LayYear <- factor(temp$LayYear)
temp[,'Survived to following year?'] <- ifelse(temp$SurvivedNext == 1,'Y','N')

Fig4B <- ggplot(temp,
       aes(x = LayYear,
           y = RTL,
           fill = `Survived to following year?`)) +
  xlab('Cohort') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = 'top') +
  geom_boxplot(outlier.shape = NA,alpha = 0.2)+
  geom_jitter(aes(col = `Survived to following year?`),position=position_jitterdodge(jitter.width = 0.2))+
  annotate('text',x = 0.5,y = 1.5,label = 'B')

Fig4B

>>>>

Fig1A <- ggplot(temp,aes(x = Agemonths,y = RTL))+
  ylab('RTL') + 
  xlab('Age (months)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none')+
  geom_point(col='grey')+
  stat_smooth(method = 'lm',col='darkgrey')+
  annotate('text',x = 1,y = 2.1,label = 'A')

@@

Fig1B <- ggplot(temp,aes(x = DeltaAge,y = RTL))+
  ylab('RTL') + 
  xlab(expression(Delta*' age (months)')) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none')+
  geom_point(col='grey')+
  stat_smooth(method = 'lm',col = 'darkgrey')+
  annotate('text',x = -100,y = 2.1,label = 'B')

@@

Fig2 <- ggplot(temp,aes(x = LayYear,y = RTL))+
  ylab('RTL') + 
  xlab('Cohort') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12,angle = 90), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'top')+
  geom_jitter(col = 'grey')+
  geom_boxplot(outlier.colour = NA,notch=F,alpha=0)

@@

Fig3A <- forestplot(table2)+
  annotate('text',x = 0.6,y = 0.25,label = 'A')+
  theme(axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'))

@@

Fig3B <- ggplot(temp,
       aes(x = Tarsus,
           y = RTL,
           colour=`Age (months)`,
           fill = `Age (months)`,
           shape = `Age (months)`)) +
  ylab('RTL') + 
  xlab('Tarsus length (mm)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'top') +
  geom_point()+
  stat_smooth(method = 'lm')+
  scale_colour_manual(values = c('grey','darkorange','darkgreen'))+
  scale_fill_manual(values = c('grey','darkorange','darkgreen'))+
  annotate('text',x = 17,y = 2.1,label = 'B')

Fig3C <- ggplot(temp,
       aes(col = `Age (months)`,
           fill =  `Age (months)`,
           y = RTL,
           x=TQ)) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'top') +
  geom_point()+
  stat_smooth(method = 'lm')+
  scale_colour_manual(values = c('grey','darkorange','darkgreen'))+
  scale_fill_manual(values = c('grey','darkorange','darkgreen'))+
  annotate('text',x = 3,y = 2.1,label = 'C')

@@

Fig4A <- ggplot(temp,
       aes(x = RTL,
           y = RTL1)) +
  ylab('Adult RTL') + 
  xlab('Juvenile RTL') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = c(0.82,0.88),
        legend.title = element_text(size = 12),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.background = element_rect(fill = grey(0.9))) +
  geom_point(col='grey')+
  stat_smooth(method = 'lm',col='darkgrey')+
  annotate('text',x = 0,y = 1.8,label = 'A')

temp <- subset(dd,DeltaAge !=0)
reps <- tapply(temp$RTL,temp$BirdID,length)
keep <- names(reps[reps>3])
temp <- subset(temp,BirdID %in% keep)

mins <- tapply(temp$Agemonths,temp$BirdID,min)
keep2 <- names(mins[mins <5])
temp <- subset(temp,BirdID %in% keep2)
temp <- subset(temp,!duplicated(paste0(BirdID,Agemonths)))

Fig4B <- ggplot(temp,aes(x = Agemonths,y = RTL,group = BirdID,col=factor(BirdID)))+
geom_point()+
geom_line()+
  xlab('Age (months)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none')+
  annotate('text',x = -5,y = 2,label = 'B')

temp <- Loss
#Run the model
lm2 <- lmer(Loss ~ Agemonths+Helper+Tarsus + NonHelper + Sex + BodyMass  + TQ + (1|FieldPeriodID) + (1|TerritoryID),
            data = temp,
            REML = FALSE)
lm2 <- standardize(lm2)

@@

Fig4C <- forestplot(table2)+
  annotate('text',x = 0.55,y = 0.6,label = 'C')+
  theme(        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'))

@@

temp <- subset(dd,DeltaAge !=0)
reps <- tapply(temp$RTL,temp$BirdID,length)
keep <- names(reps[reps>3])
temp <- subset(temp,BirdID %in% keep)

mins <- tapply(temp$Agemonths,temp$BirdID,min)
keep2 <- names(mins[mins <5])
temp <- subset(temp,BirdID %in% keep2)
temp <- subset(temp,!duplicated(paste0(BirdID,Agemonths)))

ggplot(temp,aes(x = Agemonths,y = RTL,group = BirdID,col=factor(BirdID)))+
geom_point()+
geom_line()+
theme(legend.position='none')
